### 2013-11-19 finalPlots.Rmd
Some basic fixing since Moscow conference. DV table fixed, analysis cleared. Baseline for trying out some more modelling after Moscow discussions.

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knit("finalPlots.Rmd")
system("pandoc -s finalPlots.md -o finalPlots.html --toc --number-section")

@@

#########################################
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
```

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(kaRski)
knit("finalPlots.Rmd")
system("pandoc -s finalPlots.md -o finalPlots.html --toc --number-section")

@@

#########################################
load("~/workspace/lits/attributions/data/lits.RData")

### 2013-11-19 mapPlots.Rmd
Some basic fixing since Moscow conference. DV table fixed, analysis cleared. Baseline for trying out some more modelling after Moscow discussions.

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("mapPlots.Rmd")
system("pandoc -s mapPlots.md -o mapPlots.html --toc --number-section")
```

@@

```{rmapPlotsLoadData}
library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit("mapPlots.Rmd")
system("pandoc -s mapPlots.md -o mapPlots.html --toc --number-section")
```

@@

```{rmapPlotsLoadData}
library(RColorBrewer)
library(mapproj)
library(maptools)
library(rgdal)
load("~/workspace/lits/attributions/data/lits.RData")
map <- suppressWarnings(readOGR(dsn="/home/aurelius/workspace/data/shapefiles/lits/", 
                                layer="lits_all_simple"))
